% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Wenqi Xu}

\basicInfo{
  \email{xuw63@mcmaster.ca} \textperiodcentered\ 
  \phone{(+1) 905-962-5206} \textperiodcentered\ 
  \linkedin[wenqixu]{https://www.linkedin.com/in/wenqixu}
  \textperiodcentered\ 
  \github[wenqi95]{https://github.com/wenqi95}}

\section{Education}
\datedsubsection{\textbf{McMaster University}, Hamilton, ON}{Sep. 2017 - May. 2019(Exp)}
\textit{Master of Engineering} in Software Engineering(\textbf{Co-op program})\\
\textbf{Courses: }Analysis of Algorithms, Web Applications, Mobile Data Analytics, Big Data Systems

\datedsubsection{\textbf{Southeast University}, Nanjing, China}{Sep. 2013 - Jun. 2017}
\textit{Bachelor of Engineering} in Electrical \& Computer Engineering\\
\textbf{Courses: }Object-Oriented Programming, Operating Systems, Computer Networks, Computer Vision

\section{Skills}
\begin{itemize}[parsep=0.5ex]
  \item \textbf{Languages: }Java, Python, C, C++, Golang, JavaScript, SQL, MATLAB, HTML, CSS
  \item \textbf{Technologies: }Linux, Web Development, Machine Learning(scikit-learn), Git, Node.js, AWS, Spark
\end{itemize}



\section{Experience}
\datedsubsection{\textbf{Key-Value Database Server} }{Jan. 2018}

\begin{itemize}
  \item  Implemented a centralized database server and replicated servers with in-memory database in Golang 
  \item Dealt with concurrent read/write requests from multiple clients, which also keeps clients' data consistent with server's database
  \item A practical application for this is a set of replicated web servers that have eventually-consistent distributed in-memory state loaded from a centralized key-value store
\end{itemize}

\datedsubsection{\textbf{Location Based Information Service Website}}{Feb. 2018}
\begin{itemize}
    \item Built a website that users can add new locations (geolocations, upload pictures) and add reviews to locations
    \item Implemented features using HTML, CSS, Bootstrap, PHP, MySQL and Apache
    \item Deployed the web applications to AWS EC2 instance
\end{itemize}



\datedsubsection{\textbf{Taxi Data Analysis and Demand Prediction}}{Sep. 2017}
\begin{itemize}
  \item Built a taxi demand prediction system using Spark MLlib that could predict taxi demand based on location, time and weather condition
  \item Wrote python scripts to process over one million NYC taxi data and extract features
  \item Applied random forest regression model to make prediction and evaluated this model by computing RMSE
\end{itemize}

\datedsubsection{\textbf{Image Processing Algorithm using Java}}{Aug. 2017}
\begin{itemize}
    \item Implemented the seam carving algorithm for content-aware image resizing using Java
    \item Proposed and tested improved methods on content amplification and object removing
\end{itemize}



\datedsubsection{\textbf{Indoor Positioning System based on WiFi Fingerprint Data}}{May. 2016}
\begin{itemize}
  \item Trained a GP regression model with RSS data and use MAP estimation to determine the location
  \item  Implemented a particle filter that incorporates IMU measurements and a given map to track a moving device
  \item Using python matplotlib to visualize the positioning results
\end{itemize}








% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 20a15}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}
\section{Honors and Awards}
\datedline{First Prize in National Mathematical Contest in Modelling }{Oct. 2016}
\datedline{Excellent Undergraduate Fellowship (For Top 3\%)}{Jan. 2016}
\datedline{Outstanding Student Leader Scholarship (For Top 10\%)}{May. 2015}








%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
